---
title: "MV2_exploratory analysis"
output: html_document
date: "2026-04-14"
---

1. Load relevant packages
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(broom)
library(reshape2)
library(ggdist)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(patchwork)
library(tidyr)
library(ggcorrplot)
library(MuMIn)
library(effsize)
library(ggExtra)
library(gridExtra)
library(irr)
library(psych)
```

2. Read the form (it has been cleaned)
```{r}
mv2 <- read.csv("/Users/betty/Desktop/Manyvoices2/stage2data.csv")
```

3. Rename the first-row question labels to shorter variable names for ease of processing.
```{r}
# Rename the pre-experiment questions
colnames(mv2)
colnames(mv2)[22] <- "Pre_enjoyment_singing"
colnames(mv2)[23] <- "Pre_bonding_trust"
colnames(mv2)[24] <- "Pre_enjoyment_speaking"
colnames(mv2)[25] <- "Pre_bonding_sameteam"
colnames(mv2)[26] <- "Pre_embarrassment_singing"
colnames(mv2)[27] <- "Pre_bonding_similar"
colnames(mv2)[28] <- "Pre_embarrassment_speaking"
colnames(mv2)[29] <- "Pre_bonding_ties"
colnames(mv2)[30] <- "Pre_bonding_common"
colnames(mv2)[31] <- "Pre_outgoing"
colnames(mv2)[32] <- "Pre_bonding_closeness"

# Rename the post-experiment questions
colnames(mv2)[33] <- "Post_difficult_task"
colnames(mv2)[34] <- "Post_bonding_trust"
colnames(mv2)[35] <- "Post_enjoyment_task"
colnames(mv2)[36] <- "Post_bonding_sameteam"
colnames(mv2)[37] <- "Post_embarrassment_task"
colnames(mv2)[38] <- "Post_bonding_similar"
colnames(mv2)[39] <- "Post_follow_instruction"
colnames(mv2)[40] <- "Post_synchronization"
colnames(mv2)[41] <- "Post_bonding_ties"
colnames(mv2)[42] <- "Post_attention_check"
colnames(mv2)[43] <- "Post_bonding_common"
colnames(mv2)[44] <- "Post_leader"
colnames(mv2)[45] <- "Post_bonding_closeness"
colnames(mv2)[46] <- "Public_goods_game"
colnames(mv2)[47] <- "Goal_experiment"

#Rename the final-experiment questions
colnames(mv2)[48] <- "Final_difficult_task"
colnames(mv2)[49] <- "Final_bonding_trust"
colnames(mv2)[50] <- "Final_enjoyment_task"
colnames(mv2)[51] <- "Final_bonding_sameteam"
colnames(mv2)[52] <- "Final_embarrassment_task"
colnames(mv2)[53] <- "Final_bonding_similar"
colnames(mv2)[54] <- "Final_follow_instruction"
colnames(mv2)[55] <- "Final_synchronization"
colnames(mv2)[56] <- "Final_bonding_ties"
colnames(mv2)[57] <- "Final_bonding_common"
colnames(mv2)[58] <- "Final_leader"
colnames(mv2)[59] <- "Final_bonding_closeness"

#Rename demographic information questions
colnames(mv2)[60] <- "Age"
colnames(mv2)[61] <- "Gender_choice"
colnames(mv2)[62] <- "Gender_text"
colnames(mv2)[63] <- "Native_language"
colnames(mv2)[64] <- "Ethnicity"
colnames(mv2)[65] <- "Religion"
colnames(mv2)[66] <- "City_experiment"
colnames(mv2)[67] <- "Birthplace"
colnames(mv2)[68] <- "Musicianship(self-perceived)"
colnames(mv2)[69] <- "Musicianship(complimented)"
colnames(mv2)[70] <- "Know_song"
colnames(mv2)[71] <- "Like_song"
colnames(mv2)[72] <- "Sing_regularly"
colnames(mv2)[73] <- "Training_singing"
colnames(mv2)[74] <- "Training_instrument"
colnames(mv2)[75] <- "Instrument_list"
colnames(mv2)[76] <- "Number_meet_participants"
colnames(mv2)[77] <- "Rate_familiarity"
colnames(mv2)[78] <- "Comment_study"

colnames(mv2)
```

4. Preprocessing
4.1 Preprocessing - classifying the data in terms of the city that experiments performed
```{r}
# Classifying data in terms of language and location
mv2$Language <- NA
mv2$Location <- NA

#1.Row 1-25 = Mandarin, London
mv2$Language[1:25] <- "Mandarin"
mv2$Location[1:25] <- "London"
#2.Row 26-55 = Bahasa Indonesian, Solo
mv2$Language[26:55] <- "Bahasa Indonesia"
mv2$Location[26:55] <- "Solo"
#3.Row 56-70 = Japanese, Tokyo
mv2$Language[56:70] <- "Japanese"
mv2$Location[56:70] <- "Tokyo"
#4.Row 71-85; 102-110 = Romanian, Cluj-Napoca
mv2$Language[71:85] <- "Romanian"
mv2$Location[71:85] <- "Cluj-Napoca"
mv2$Language[102:110] <- "Romanian"
mv2$Location[102:110] <- "Cluj-Napoca"
#5.Row 86-101 = Hindi, New Delhi
mv2$Language[86:101] <- "Hindi"
mv2$Location[86:101] <- "New Delhi"
#6.Row 111-130 = Mandarin, Auckland
mv2$Language[111:130] <- "Mandarin"
mv2$Location[111:130] <- "Auckland"
#7.Row 131-152;182 = English, Auckland
mv2$Language[131:152] <- "English"
mv2$Location[131:152] <- "Auckland"
mv2$Language[182] <- "English"
mv2$Location[182] <- "Auckland"
#8.Row 153-181 = Italian, Padua
mv2$Language[153:181] <- "Italian"
mv2$Location[153:181] <- "Padua"
#9.Row 183-188;258-263;293-298 = Italian, Rome
mv2$Language[183:188] <- "Italian"
mv2$Location[183:188] <- "Rome"
mv2$Language[258:263] <- "Italian"
mv2$Location[258:263] <- "Rome"
mv2$Language[293:298] <- "Italian"
mv2$Location[293:298] <- "Rome"
#10.Row 189-211 = Czech, Prague
mv2$Language[189:211] <- "Czech"
mv2$Location[189:211] <- "Prague"
#11.Row 212-239 = Thai, Bangkok
mv2$Language[212:239] <- "Thai"
mv2$Location[212:239] <- "Bangkok"
#12.Row 240-257 = Mandarin, Reading
mv2$Language[240:257] <- "Mandarin"
mv2$Location[240:257] <- "Reading"
#13.Row 264-292 = Yoruba, Lagos
mv2$Language[264:292] <- "Yoruba"
mv2$Location[264:292] <- "Lagos"
#14.Row 299-319 = German, Frankfurt
mv2$Language[299:319] <- "German"
mv2$Location[299:319] <- "Frankfurt"
#15.Row 320-343 = Norwegian, Bergen
mv2$Language[320:343] <- "Norwegian"
mv2$Location[320:343] <- "Bergen"
#16.Row 344-368 = Spanish, Bogotá
mv2$Language[344:368] <- "Spanish"
mv2$Location[344:368] <- "Bogotá"
#17.Row 369-394 = English, Toronto
mv2$Language[369:394] <- "English"
mv2$Location[369:394] <- "Toronto"
#18.Row 439-453;470-478 = German, Innsbruck. 
mv2$Language[439:453] <- "German"
mv2$Location[439:453] <- "Innsbruck"
mv2$Language[470:478] <- "German"
mv2$Location[470:478] <- "Innsbruck"
#19.Row 395-400;406-410;454-458 = English, Nottingham
mv2$Language[395:400] <- "English"
mv2$Location[395:400] <- "Nottingham"
mv2$Language[406:410] <- "English"
mv2$Location[406:410] <- "Nottingham"
mv2$Language[454:458] <- "English"
mv2$Location[454:458] <- "Nottingham"
#20.Row 401-405;433-438;479-483 = English, Gold Coast
mv2$Language[401:405] <- "English"
mv2$Location[401:405] <- "Gold Coast"
mv2$Language[433:438] <- "English"
mv2$Location[433:438] <- "Gold Coast"
mv2$Language[479:483] <- "English"
mv2$Location[479:483] <- "Gold Coast"
#21.Row 411-432 = Russian, London
mv2$Language[411:432] <- "Russian"
mv2$Location[411:432] <- "London"
#22.Row 459-469;490-495 = English, Buffalo
mv2$Language[459:469] <- "English"
mv2$Location[459:469] <- "Buffalo"
mv2$Language[490:495] <- "English"
mv2$Location[490:495] <- "Buffalo"
#23.Row 484-489;496-503;521-526 = Te Reo Māori, Auckland
mv2$Language[484:489] <- "Māori"
mv2$Location[484:489] <- "Auckland"
mv2$Language[496:503] <- "Māori"
mv2$Location[496:503] <- "Auckland"
mv2$Language[521:526] <- "Māori"
mv2$Location[521:526] <- "Auckland"
#24.Row 504-520;527-532 = Hungarian, Budapest
mv2$Language[504:520] <- "Hungarian"
mv2$Location[504:520] <- "Budapest"
mv2$Language[527:532] <- "Hungarian"
mv2$Location[527:532] <- "Budapest"
#25.Row 533-561 = Russian, Yekaterinburg
mv2$Language[533:561] <- "Russian"
mv2$Location[533:561] <- "Yekaterinburg"
#26.Row 562-585 = Polish, Poland
mv2$Language[562:585] <- "Polish"
mv2$Location[562:585] <- "Poland"
#27.Row 586-609 = Western Farsi, Kaiserslautern
mv2$Language[586:609] <- "Western Farsi"
mv2$Location[586:609] <- "Kaiserslautern"
#28.Row 610-637 = Korean, South Korea
mv2$Language[610:637] <- "Korean"
mv2$Location[610:637] <- "South Korea"
#29.Row 638-660 = Georgian, Georgia
mv2$Language[638:660] <- "Georgian"
mv2$Location[638:660] <- "Georgia"
#30.Row 661-684 = English, Hamilton
mv2$Language[661:684] <- "English"
mv2$Location[661:684] <- "Hamilton"
#31.Row 685-694 = English, Boston
mv2$Language[685:694] <- "English"
mv2$Location[685:694] <- "Boston"
mv2$Language[732:736] <- "English"
mv2$Location[732:736] <- "Boston"
#32.Row 695-718 = Finnish, Jyväskylä
mv2$Language[695:718] <- "Finnish"
mv2$Location[695:718] <- "Jyväskylä"
#33.Row 719-731 = French, Saint-Étienne
mv2$Language[719:731] <- "French"
mv2$Location[719:731] <- "Saint-Étienne"
mv2$Language[772:781] <- "French"
mv2$Location[772:781] <- "Saint-Étienne"
#34.Row 737-764 = Sinhala, Sri Lanka
mv2$Language[737:764] <- "Sinhala"
mv2$Location[737:764] <- "Sri Lanka"
#35.Row 765-771;782-798 = Dutch, Nijmegen
mv2$Language[765:771] <- "Dutch"
mv2$Location[765:771] <- "Nijmegen"
mv2$Language[782:798] <- "Dutch"
mv2$Location[782:798] <- "Nijmegen"
#36.Row 799-814;919-926;981 = Greek, Greece
mv2$Language[799:814] <- "Greek"
mv2$Location[799:814] <- "Greece"
mv2$Language[919:926] <- "Greek"
mv2$Location[919:926] <- "Greece"
mv2$Language[981] <- "Greek"
mv2$Location[981] <- "Greece"
#37.Row 815-842 = Danish, Denmark
mv2$Language[815:842] <- "Danish"
mv2$Location[815:842] <- "Denmark"
#38.Row 815-842 = Bulgarian, Bulgaria
mv2$Language[843:863] <- "Bulgarian"
mv2$Location[843:863] <- "Bulgaria"
#39.Row 864-892;927 = Fante, Ghana
mv2$Language[864:892] <- "Fante"
mv2$Location[864:892] <- "Ghana"
mv2$Language[927] <- "Fante"
mv2$Location[927] <- "Ghana"
#40.Row 893-899;971-980 = German, Vienna
mv2$Language[893:899] <- "German"
mv2$Location[893:899] <- "Vienna"
mv2$Language[971:980] <- "German"
mv2$Location[971:980] <- "Vienna"
#41.Row 900-918 = Mandarin, Ann arbor
mv2$Language[900:918] <- "Mandarin"
mv2$Location[900:918] <- "Ann Arbor"
#42.Row 928-953 = Shipibo-Konibo, Perú
mv2$Language[928:953] <- "Shipibo-Konibo"
mv2$Location[928:953] <- "Perú"
#43.Row 954-969;982-991 = IsiZulu, South Africa
mv2$Language[954:970] <- "IsiZulu"
mv2$Location[954:970] <- "South Africa"
mv2$Language[982:991] <- "IsiZulu"
mv2$Location[982:991] <- "South Africa"
```


4.2 Preprocessing - add Language and Location for experimenlog.csv
```{r}
mv2_experimenterlog <- read.csv("/Users/betty/Desktop/Manyvoices2/experimentlog.csv")

# Classifying data in terms of language and location
mv2_experimenterlog$Language <- NA
mv2_experimenterlog$Location <- NA

#1.Row 1-3 = Mandarin, London
mv2_experimenterlog$Language[1:3] <- "Mandarin"
mv2_experimenterlog$Location[1:3] <- "London"
#2.Row 4-6 = Bahasa Indonesia, Solo
mv2_experimenterlog$Language[4:6] <- "Bahasa Indonesia"
mv2_experimenterlog$Location[4:6] <- "Solo"
#3.Row 7-9 = Japanese, Tokyo
mv2_experimenterlog$Language[7:9] <- "Japanese"
mv2_experimenterlog$Location[7:9] <- "Tokyo"
#4.Row 10-11;15 = Romanian, Cluj-Napoca
mv2_experimenterlog$Language[10:11] <- "Romanian"
mv2_experimenterlog$Location[10:11] <- "Cluj-Napoca"
mv2_experimenterlog$Language[15] <- "Romanian"
mv2_experimenterlog$Location[15] <- "Cluj-Napoca"
#5.Row 12-14 = Hindi, New Delhi
mv2_experimenterlog$Language[12:14] <- "Hindi"
mv2_experimenterlog$Location[12:14] <- "New Delhi"
#6.Row 16-18 = Mandarin, Auckland
mv2_experimenterlog$Language[16:18] <- "Mandarin"
mv2_experimenterlog$Location[16:18] <- "Auckland"
#7.Row 19-21 = English, Auckland
mv2_experimenterlog$Language[19:21] <- "English"
mv2_experimenterlog$Location[19:21] <- "Auckland"
#8.Row 22-24 = Italian, Padua
mv2_experimenterlog$Language[22:24] <- "Italian"
mv2_experimenterlog$Location[22:24] <- "Padua"
#9.Row 25;35;38 = Italian, Rome
mv2_experimenterlog$Language[25] <- "Italian"
mv2_experimenterlog$Location[25] <- "Rome"
mv2_experimenterlog$Language[35] <- "Italian"
mv2_experimenterlog$Location[35] <- "Rome"
mv2_experimenterlog$Language[38] <- "Italian"
mv2_experimenterlog$Location[38] <- "Rome"
#10.Row 26-28 = Czech, Prague
mv2_experimenterlog$Language[26:28] <- "Czech"
mv2_experimenterlog$Location[26:28] <- "Prague"
#11.Row 29-31 = Thai, Bangkok
mv2_experimenterlog$Language[29:31] <- "Thai"
mv2_experimenterlog$Location[29:31] <- "Bangkok"
#12.Row 32-34 = Mandarin, Reading
mv2_experimenterlog$Language[32:34] <- "Mandarin"
mv2_experimenterlog$Location[32:34] <- "Reading"
#13.Row 36-37;39 = Yoruba, Lagos
mv2_experimenterlog$Language[36:37] <- "Yoruba"
mv2_experimenterlog$Location[36:37] <- "Lagos"
mv2_experimenterlog$Language[39] <- "Yoruba"
mv2_experimenterlog$Location[39] <- "Lagos"
#14.Row 40-42 = German, Frankfurt
mv2_experimenterlog$Language[40:42] <- "German"
mv2_experimenterlog$Location[40:42] <- "Frankfurt"
#15.Row 43-45 = Norwegian, Bergen
mv2_experimenterlog$Language[43:45] <- "Norwegian"
mv2_experimenterlog$Location[43:45] <- "Bergen"
#16.Row 46-48 = Spanish, Bogotá
mv2_experimenterlog$Language[46:48] <- "Spanish"
mv2_experimenterlog$Location[46:48] <- "Bogotá"
#17.Row 49-51 = English, Toronto
mv2_experimenterlog$Language[49:51] <- "English"
mv2_experimenterlog$Location[49:51] <- "Toronto"
#18.Row 52;54;61 = English, Nottingham
mv2_experimenterlog$Language[52] <- "English"
mv2_experimenterlog$Location[52] <- "Nottingham"
mv2_experimenterlog$Language[54] <- "English"
mv2_experimenterlog$Location[54] <- "Nottingham"
mv2_experimenterlog$Language[61] <- "English"
mv2_experimenterlog$Location[61] <- "Nottingham"
#19.Row 53;58;65 = English, Gold Coast
mv2_experimenterlog$Language[53] <- "English"
mv2_experimenterlog$Location[53] <- "Gold Coast"
mv2_experimenterlog$Language[58] <- "English"
mv2_experimenterlog$Location[58] <- "Gold Coast"
mv2_experimenterlog$Language[65] <- "English"
mv2_experimenterlog$Location[65] <- "Gold Coast"
#20.Row 55-57 = Russian, London
mv2_experimenterlog$Language[55:57] <- "Russian"
mv2_experimenterlog$Location[55:57] <- "London"
#21.Row 59-60;64 = German, Innsbruck
mv2_experimenterlog$Language[59:60] <- "German"
mv2_experimenterlog$Location[59:60] <- "Innsbruck"
mv2_experimenterlog$Language[64] <- "German"
mv2_experimenterlog$Location[64] <- "Innsbruck"
#22.Row 62-63;67 = English, Buffalo
mv2_experimenterlog$Language[62:63] <- "English"
mv2_experimenterlog$Location[62:63] <- "Buffalo"
mv2_experimenterlog$Language[67] <- "English"
mv2_experimenterlog$Location[67] <- "Buffalo"
#23.Row 66;68-69 = Te Reo Māori, Auckland
mv2_experimenterlog$Language[68:69] <- "Māori"
mv2_experimenterlog$Location[68:69] <- "Auckland"
mv2_experimenterlog$Language[66] <- "Māori"
mv2_experimenterlog$Location[66] <- "Auckland"
#24.Row 70-72 = Hungarian, Budapest
mv2_experimenterlog$Language[70:72] <- "Hungarian"
mv2_experimenterlog$Location[70:72] <- "Budapest"
#25.Row 73-75 = Russian, Yekaterinburg
mv2_experimenterlog$Language[73:75] <- "Russian"
mv2_experimenterlog$Location[73:75] <- "Ekaterinburg"
#26.Row 76-78 = Polish, Poland
mv2_experimenterlog$Language[76:78] <- "Polish"
mv2_experimenterlog$Location[76:78] <- "Poland"
#27.Row 79-81 = Western Farsi, Kaiserslautern
mv2_experimenterlog$Language[79:81] <- "Western Farsi"
mv2_experimenterlog$Location[79:81] <- "Kaiserslautern"
#28.Row 82-84 = Korean, South Korea
mv2_experimenterlog$Language[82:84] <- "Korean"
mv2_experimenterlog$Location[82:84] <- "South Korea"
#29.Row 85-87 = Georgian, Georgia
mv2_experimenterlog$Language[85:87] <- "Georgian"
mv2_experimenterlog$Location[85:87] <- "Georgia"
#30.Row 88-90 = English, Hamilton
mv2_experimenterlog$Language[88:90] <- "English"
mv2_experimenterlog$Location[88:90] <- "Hamilton"
#31.Row 91-92;98 = English, Boston
mv2_experimenterlog$Language[91:92] <- "English"
mv2_experimenterlog$Location[91:92] <- "Boston"
mv2_experimenterlog$Language[98] <- "English"
mv2_experimenterlog$Location[98] <- "Boston"
#32.Row 93-95 = Finnish, Jyväskylä
mv2_experimenterlog$Language[93:95] <- "Finnish"
mv2_experimenterlog$Location[93:95] <- "Jyväskylä"
#33.Row 96-97;103 = French, Saint-Étienne
mv2_experimenterlog$Language[96:97] <- "French"
mv2_experimenterlog$Location[96:97] <- "Saint-Étienne"
mv2_experimenterlog$Language[103] <- "French"
mv2_experimenterlog$Location[103] <- "Saint-Étienne"
#34.Row 100-102 = Sinhala, Sri Lanka
mv2_experimenterlog$Language[100:102] <- "Sinhala"
mv2_experimenterlog$Location[100:102] <- "Sri Lanka"
#35.Row 99;104-105 = Dutch, Nijmegen
mv2_experimenterlog$Language[99] <- "Dutch"
mv2_experimenterlog$Location[99] <- "Nijmegen"
mv2_experimenterlog$Language[104:105] <- "Dutch"
mv2_experimenterlog$Location[104:105] <- "Nijmegen"
#36.Row 106-107;121 = Greek, Greece
mv2_experimenterlog$Language[106:107] <- "Greek"
mv2_experimenterlog$Location[106:107] <- "Greece"
mv2_experimenterlog$Language[121] <- "Greek"
mv2_experimenterlog$Location[121] <- "Greece"
#37.Row 108-110 = Danish, Denmark
mv2_experimenterlog$Language[108:110] <- "Danish"
mv2_experimenterlog$Location[108:110] <- "Denmark"
#38.Row 111-113 = Bulgarian, Bulgaria
mv2_experimenterlog$Language[111:113] <- "Bulgarian"
mv2_experimenterlog$Location[111:113] <- "Bulgaria"
#39.Row 114-116 = Fante, Ghana
mv2_experimenterlog$Language[114:116] <- "Fante"
mv2_experimenterlog$Location[114:116] <- "Ghana"
#40.Row 117;126-127 = German, Vienna
mv2_experimenterlog$Language[117] <- "German"
mv2_experimenterlog$Location[117] <- "Vienna"
mv2_experimenterlog$Language[126:127] <- "German"
mv2_experimenterlog$Location[126:127] <- "Vienna"
#41.Row 118-120 = Mandarin, Ann arbor
mv2_experimenterlog$Language[118:120] <- "Mandarin"
mv2_experimenterlog$Location[118:120] <- "Ann arbor"
#42.Row 122-123;128 = Shipibo-Konibo, Perú
mv2_experimenterlog$Language[122:123] <- "Shipibo-Konibo"
mv2_experimenterlog$Location[122:123] <- "Perú"
mv2_experimenterlog$Language[128] <- "Shipibo-Konibo"
mv2_experimenterlog$Location[128] <- "Perú"
#43.Row 124-125;129 = IsiZulu, South Africa
mv2_experimenterlog$Language[124:125] <- "IsiZulu"
mv2_experimenterlog$Location[124:125] <- "South Africa"
mv2_experimenterlog$Language[129] <- "IsiZulu"
mv2_experimenterlog$Location[129] <- "South Africa"
```

4.3 Preprocessing - rename experiment.condition & Num_of_participants & group in experimenterlog as CRS
```{r}
# Rename condition as CRS
mv2_experimenterlog <- mv2_experimenterlog %>%
  mutate(Experiment.condition = case_when(
    Experiment.condition == "Conversation first" ~ "C",
    Experiment.condition == "Recitation first" ~ "R",
    Experiment.condition == "Singing first" ~ "S",
    TRUE ~ as.character(Experiment.condition)
  )) %>%
print()
# Rename column name Num_of_participants and group
colnames(mv2_experimenterlog)
colnames(mv2_experimenterlog)[24] <- "Num_of_participants"
colnames(mv2_experimenterlog)[23] <- "group"
colnames(mv2_experimenterlog)
```

4.4 Preprocessing mv2 - Calculate the bonding score (Post-Pre); (Final-Pre); (Final-Post); 
Excluding rows that pre-bonding score > 80 and attention check < 50. 
```{r}
# Calculate pre_bonding_score
mv2 <- mv2 %>%
  mutate(pre_bonding_score = (
    Pre_bonding_trust +
    Pre_bonding_sameteam +
    Pre_bonding_similar +
    Pre_bonding_ties +
    Pre_bonding_common +
    Pre_bonding_closeness
  ) / 6)
# Calculate post_bonding_score
mv2 <- mv2 %>%
  mutate(post_bonding_score = (
    Post_bonding_trust +
    Post_bonding_sameteam +
    Post_bonding_similar +
    Post_bonding_ties +
    Post_bonding_common +
    Post_bonding_closeness
  ) / 6)
# Calculate final_bonding_score
mv2 <- mv2 %>%
  mutate(final_bonding_score = (
    Final_bonding_trust +
    Final_bonding_sameteam +
    Final_bonding_similar +
    Final_bonding_ties +
    Final_bonding_common +
    Final_bonding_closeness
  ) / 6)
# Calculate difference between post-pre and final-post
mv2 <- mv2 %>%
  mutate(bonding_post_pre_difference = post_bonding_score - pre_bonding_score,
        bonding_final_post_difference = final_bonding_score - post_bonding_score,
        bonding_final_pre_difference = final_bonding_score - pre_bonding_score)
cat("Number of rows with pre_bonding_score > 80:", sum(mv2$pre_bonding_score > 80, na.rm = TRUE), "\n")
cat("Number of rows with Post_attention_check < 50:", sum(mv2$Post_attention_check < 50, na.rm = TRUE), "\n")

mv2 <- mv2 %>%
  filter(
    pre_bonding_score <= 80,
    Post_attention_check >= 50
  ) 

cat("Remaining rows in mv2:", nrow(mv2), "\n")
```

4.5 Preprocessing - Combine two forms (mv2 & experimenterlog) based on Language Location and group
```{r}
mv2_bonding_score <- mv2 %>%
  group_by(Language, Location, group) %>%
  summarise(
    mean_bonding_post_pre_difference = mean(bonding_post_pre_difference, na.rm = TRUE),
    mean_bonding_final_post_difference = mean(bonding_final_post_difference, na.rm = TRUE),
    mean_bonding_final_pre_difference = mean(bonding_final_pre_difference, na.rm = TRUE),
    .groups = "drop"
  )
mv2_groupsize <- mv2_bonding_score %>%
  left_join(mv2_experimenterlog, 
            by = c("Language", "Location", "group"))

groupsize_lookup <- mv2_experimenterlog %>%
  dplyr::select(Language, Location, group, Num_of_participants) %>%
  distinct()  
mv2 <- mv2 %>%
  left_join(groupsize_lookup, by = c("Language", "Location", "group"))

cat("Number of rows after merging:", nrow(mv2), "\n")
cat("Group size distribution:\n")
print(table(mv2$Num_of_participants))

dir.create("/Users/betty/Desktop/Manyvoices2/Results/Table", 
           recursive = TRUE, showWarnings = FALSE)
write.csv(mv2, file = "/Users/betty/Desktop/Manyvoices2/Results/Table/mv2_cleaned.csv", 
          row.names = FALSE) 
```
5. Exploratorary analysis - cross cultural variation in vocalisation-bonding relationship

5.1 This can be used for creating Figure 6 in main text & Figure S5-S6 in supplemenrtary materials. 
```{r}


group_colors <- c("C" = "#D95F02", "S" = "#1B9E77", "R" = "#7570B3")
group_labels <- c("C" = "Conversation", "S" = "Singing", "R" = "Recitation")

mv2 %>%
  filter(!is.na(pre_bonding_score), !is.na(post_bonding_score), !is.na(group)) %>%
  mutate(
    site = paste(Language, Location, sep = " - "),
    pct_change = ifelse(pre_bonding_score > 0,
                        (post_bonding_score - pre_bonding_score) / pre_bonding_score * 100,
                        NA) 
  ) %>%
  group_by(site, group) %>%
  summarise(
    mean_pre  = round(mean(pre_bonding_score,  na.rm = TRUE), 2),
    mean_post = round(mean(post_bonding_score, na.rm = TRUE), 2),
    mean_diff = round(mean(post_bonding_score - pre_bonding_score, na.rm = TRUE), 2),
    mean_pct  = round(mean(pct_change, na.rm = TRUE), 1), 
    n         = n(),
    .groups   = "drop"
  )

site_data <- mv2 %>%
  filter(!is.na(pre_bonding_score), !is.na(post_bonding_score), !is.na(group)) %>%
  mutate(
    site = paste(Language, Location, sep = " - "),
    site_label = ifelse(
      Language %in% c("English", "Mandarin", "German", "Russian", "Spanish", "Italian"),
      paste0(Language, " [", Location, "]"),
      Language
    )
  ) %>%
  group_by(site, site_label, group) %>%
  summarise(
    mean_pre  = mean(pre_bonding_score,  na.rm = TRUE),
    mean_post = mean(post_bonding_score, na.rm = TRUE),
    n         = n(),
    .groups   = "drop"
  ) %>%
  mutate(
    mean_diff = round((mean_post - mean_pre) / mean_pre * 100, 1)  # ← 用组均值算
  )

site_order <- site_data %>%
  filter(group == "S") %>%
  arrange(mean_diff) %>%
  pull(site)

site_label_map <- site_data %>%
  distinct(site, site_label)

site_data <- site_data %>%
  mutate(site = factor(site, levels = site_order))

label_order <- site_label_map$site_label[match(site_order, site_label_map$site)]

# Figure 6 - Percentage change
ggplot(site_data, aes(x = mean_diff, y = site, color = group)) +
  geom_hline(yintercept = 1:length(levels(site_data$site)),
             color = "grey85", linewidth = 0.4, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(
    size = 5, shape = 16, alpha = 0.65
  ) +
  scale_color_manual(
  values = group_colors,
  labels = group_labels,
  breaks = c("S", "C", "R")
) +
  scale_y_discrete(labels = setNames(label_order, site_order)) +
  labs(
  x     = "Percentage Change in Bonding Score (Pre- to Post-Intervention) (%)",
  color = "Group"
) +
  theme_classic() +
  theme(
    axis.text.y  = element_text(size = 16, face = "bold", color = "black"),
    axis.text.x  = element_text(size = 18),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_blank(),
    legend.title = element_text(face = "bold", size = 17),
    legend.text  = element_text(size = 16),
    legend.spacing.y = unit(0.5, "cm"), 
    legend.key.height = unit(1, "cm"),
    panel.border = element_blank(),
    axis.line    = element_blank()
  )

dir.create("/Users/betty/Desktop/Manyvoices2/Results/Figure", 
           recursive = TRUE, showWarnings = FALSE)
ggsave(
  "/Users/betty/Desktop/Manyvoices2/Results/Figure/site_bonding_diff.png",
  width = 10, height = 12, dpi = 300
)

# Figure S5 - Raw difference（Post - Pre）
site_data_raw <- mv2 %>%
  filter(!is.na(pre_bonding_score), !is.na(post_bonding_score), !is.na(group)) %>%
  mutate(
    site = paste(Language, Location, sep = " - "),
    site_label = ifelse(
      Language %in% c("English", "Mandarin", "German", "Russian", "Spanish", "Italian"),
      paste0(Language, " [", Location, "]"),
      Language
    )
  ) %>%
  group_by(site, site_label, group) %>%
  summarise(
    mean_pre  = mean(pre_bonding_score,  na.rm = TRUE),
    mean_post = mean(post_bonding_score, na.rm = TRUE),
    n         = n(),
    .groups   = "drop"
  ) %>%
  mutate(
    mean_diff = round(mean_post - mean_pre, 2)  # ← raw difference
  )

site_order_raw <- site_data_raw %>%
  filter(group == "S") %>%
  arrange(mean_diff) %>%
  pull(site)

site_label_map_raw <- site_data_raw %>%
  distinct(site, site_label)

site_data_raw <- site_data_raw %>%
  mutate(site = factor(site, levels = site_order_raw))

label_order_raw <- site_label_map_raw$site_label[match(site_order_raw, site_label_map_raw$site)]

ggplot(site_data_raw, aes(x = mean_diff, y = site, color = group)) +
  geom_hline(yintercept = 1:length(levels(site_data_raw$site)),
             color = "grey85", linewidth = 0.4, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(
    size = 5, shape = 16, alpha = 0.65
  ) +
  scale_color_manual(
  values = group_colors,
  labels = group_labels,
  breaks = c("S", "C", "R")
) +
  scale_y_discrete(labels = setNames(label_order_raw, site_order_raw)) +
  labs(
    x     = "Mean Bonding Score Change (Post - Pre)",
    color = "Group"
  ) +
  theme_classic() +
  theme(
    axis.text.y      = element_text(size = 16, face = "bold", color = "black"),
    axis.text.x      = element_text(size = 18),
    axis.title.x     = element_text(size = 18, face = "bold"),
    axis.title.y     = element_blank(),
    legend.title     = element_text(face = "bold", size = 17),
    legend.text      = element_text(size = 16),
    legend.spacing.y = unit(0.5, "cm"),
    legend.key.height = unit(1, "cm"),
    panel.border     = element_blank(),
    axis.line        = element_blank()
  )

ggsave(
  "/Users/betty/Desktop/Manyvoices2/Results/Figure/site_bonding_raw_diff.png",
  width = 10, height = 12, dpi = 300
)

#Figure S6 - Cohen' D version 
site_data <- mv2 %>%
  filter(!is.na(pre_bonding_score), !is.na(post_bonding_score), !is.na(group)) %>%
  mutate(
    site = paste(Language, Location, sep = " - "),
    site_label = ifelse(
      Language %in% c("English", "Mandarin", "German", "Russian", "Spanish", "Italian"),
      paste0(Language, " [", Location, "]"),
      Language
    )
  ) %>%
  group_by(site, site_label, group) %>%
  summarise(
    mean_pre  = mean(pre_bonding_score,  na.rm = TRUE),
    mean_post = mean(post_bonding_score, na.rm = TRUE),
    sd_pre    = sd(pre_bonding_score,    na.rm = TRUE),
    sd_post   = sd(post_bonding_score,   na.rm = TRUE),
    n         = n(),
    .groups   = "drop"
  ) %>%
  mutate(
    pooled_sd = sqrt((sd_pre^2 + sd_post^2) / 2),
    mean_diff = round((mean_post - mean_pre) / pooled_sd, 2)  # ← Cohen's d
  )

site_order <- site_data %>%
  filter(group == "S") %>%
  arrange(mean_diff) %>%
  pull(site)

site_label_map <- site_data %>%
  distinct(site, site_label)

site_data <- site_data %>%
  mutate(site = factor(site, levels = site_order))

label_order <- site_label_map$site_label[match(site_order, site_label_map$site)]

ggplot(site_data, aes(x = mean_diff, y = site, color = group)) +
  geom_hline(yintercept = 1:length(levels(site_data$site)),
             color = "grey85", linewidth = 0.4, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(size = 5, shape = 16, alpha = 0.65) +
  scale_color_manual(
  values = group_colors,
  labels = group_labels,
  breaks = c("S", "C", "R")
) +
  scale_y_discrete(labels = setNames(label_order, site_order)) +
  labs(
  x     = "Cohen's D (Pre- to Post)",
  color = "Group"
) +
  theme_classic() +
  theme(
    axis.text.y  = element_text(size = 16, face = "bold", color = "black"),
    axis.text.x  = element_text(size = 18),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_blank(),
    legend.title     = element_text(face = "bold", size = 17),
    legend.text      = element_text(size = 16),
    legend.spacing.y = unit(0.5, "cm"),
    legend.key.height = unit(1, "cm"),
    panel.border = element_blank(),
    axis.line    = element_blank()
  )

ggsave(
  "/Users/betty/Desktop/Manyvoices2/Results/Figure/site_cohend_bonding_diff.png",
  width = 10, height = 12, dpi = 300
)
```

5.2 Analysis for cross-cultural variation
```{r}
# raw difference
site_summary <- mv2 %>%
  filter(!is.na(bonding_post_pre_difference), !is.na(group)) %>%
  mutate(site = paste(Language, Location, sep = " - ")) %>%
  group_by(site, Language, Location, group) %>%
  summarise(
    mean_diff = mean(bonding_post_pre_difference, na.rm = TRUE),
    n         = n(),
    .groups   = "drop"
  )

# percentage change
site_summary_pct <- mv2 %>%
  filter(!is.na(pre_bonding_score), !is.na(post_bonding_score), !is.na(group)) %>%
  mutate(site = paste(Language, Location, sep = " - ")) %>%
  group_by(site, Language, Location, group) %>%
  summarise(
    mean_pre  = mean(pre_bonding_score,  na.rm = TRUE),
    mean_post = mean(post_bonding_score, na.rm = TRUE),
    n         = n(),
    .groups   = "drop"
  ) %>%
  mutate(mean_pct = (mean_post - mean_pre) / mean_pre * 100)


# 2. Overall consistency

cat("\n=== Angle 1: Overall consistency ===\n")
for (g in c("S", "C", "R")) {
  group_sites <- site_summary %>% filter(group == g)
  group_name  <- c("S" = "Singing", "C" = "Conversation", "R" = "Recitation")[g]
  cat("\n", group_name, "group:\n")
  cat("Total number of sites:",                         nrow(group_sites), "\n")
  cat("Number of sites with positive bonding difference:", sum(group_sites$mean_diff > 0), "\n")
  cat("Number of sites with negative bonding difference:", sum(group_sites$mean_diff < 0), "\n")
}
# Angle 2b: Cross-site variability by group (Percentage Change %)
site_summary_pct %>%
  group_by(group) %>%
  summarise(
    mean  = round(mean(mean_pct, na.rm = TRUE), 2),
    sd    = round(sd(mean_pct,   na.rm = TRUE), 2),
    min   = round(min(mean_pct,  na.rm = TRUE), 2),
    max   = round(max(mean_pct,  na.rm = TRUE), 2),
    range = round(max(mean_pct,  na.rm = TRUE) - min(mean_pct, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  print()

# Angle 3: Whether Singing is the highest of the three groups at each site

cat("\n=== Angle 3: Group ranking across sites (Percentage Change) ===\n")
site_wide <- site_summary_pct %>%
  dplyr::select(site, group, mean_pct) %>%
  tidyr::pivot_wider(names_from = group, values_from = mean_pct) %>%
  mutate(
    singing_highest      = S > C & S > R,
    singing_lowest       = S < C & S < R,
    conversation_highest = C > S & C > R,
    conversation_lowest  = C < S & C < R,
    recitation_highest   = R > S & R > C,
    recitation_lowest    = R < S & R < C
  )

cat("\nNumber of sites where Singing is highest:",      sum(site_wide$singing_highest,      na.rm = TRUE), "\n")
cat("Number of sites where Singing is lowest:",         sum(site_wide$singing_lowest,       na.rm = TRUE), "\n")
cat("\nNumber of sites where Conversation is highest:", sum(site_wide$conversation_highest, na.rm = TRUE), "\n")
cat("Number of sites where Conversation is lowest:",    sum(site_wide$conversation_lowest,  na.rm = TRUE), "\n")
cat("\nNumber of sites where Recitation is highest:",   sum(site_wide$recitation_highest,   na.rm = TRUE), "\n")
cat("Number of sites where Recitation is lowest:",      sum(site_wide$recitation_lowest,    na.rm = TRUE), "\n")

cat("\nDetails of sites where Singing is lowest:\n")
site_wide %>%
  filter(singing_lowest) %>%
  dplyr::select(site, S, C, R) %>%
  mutate(across(c(S, C, R), ~round(., 2))) %>%
  print()

#Angle 4. Western vs. Non-western
western_languages <- c("Danish", "English", "Dutch", "German", "Norwegian",
                        "Greek", "French",
                        "Italian", "Romanian", "Bulgarian", "Czech",
                        "Polish", "Russian")

site_data <- site_summary_pct %>%
  rename(pct_change = mean_pct) %>%
  mutate(
    western = ifelse(Language %in% western_languages, "Western", "Non-Western"),
    western = factor(western, levels = c("Western", "Non-Western"))
  )

cat("\nSites per group x Western/Non-Western:\n")
print(site_data %>% count(group, western))
run_ttest <- function(data, group_val) {
  d <- data %>% filter(group == group_val, !is.na(pct_change))
  if (n_distinct(d$western) < 2) {
    cat(sprintf("Skipping group %s -- only one category present.\n", group_val))
    return(NULL)
  }

  tt <- t.test(d$pct_change ~ d$western)

  d_res <- effsize::cohen.d(d$pct_change ~ d$western, hedges.correction = FALSE)
  g_res <- effsize::cohen.d(d$pct_change ~ d$western, hedges.correction = TRUE)

  tidy(tt) %>%
    mutate(
      group        = group_val,
      n_western    = sum(d$western == "Western"),
      n_nonwestern = sum(d$western == "Non-Western"),
      cohens_d     = as.numeric(d_res$estimate),
      d_CI_low     = d_res$conf.int[1],
      d_CI_high    = d_res$conf.int[2],
      hedges_g     = as.numeric(g_res$estimate),
      g_CI_low     = g_res$conf.int[1],
      g_CI_high    = g_res$conf.int[2]
    ) %>%
    rename(
      mean_western          = estimate1,
      mean_nonwestern        = estimate2,
      mean_diff_W_minus_NW  = estimate
    ) %>%
    select(group, n_western, n_nonwestern,
           mean_western, mean_nonwestern, mean_diff_W_minus_NW,
           statistic, p.value, conf.low, conf.high, method,
           cohens_d, d_CI_low, d_CI_high,
           hedges_g, g_CI_low, g_CI_high)
}

results <- bind_rows(lapply(c("S", "C", "R"), function(g) run_ttest(site_data, g)))

group_labels <- c("S" = "Singing", "C" = "Conversation", "R" = "Recitation")
results <- results %>%
  mutate(group_label = group_labels[group]) %>%
  relocate(group_label, .after = group)
print(results, width = Inf)

```


6.1 Exploratory analysis - descriptive stats for explanary variables (synchronisation, enjoyment, leadership) across three groups
```{r}
mv2 %>%
  group_by(group) %>%
  summarise(
    sync_mean   = round(mean(Post_synchronization, na.rm = TRUE), 2),
    sync_sd     = round(sd(Post_synchronization,   na.rm = TRUE), 2),
    enjoy_mean  = round(mean(Post_enjoyment_task,  na.rm = TRUE), 2),
    enjoy_sd    = round(sd(Post_enjoyment_task,    na.rm = TRUE), 2),
    leader_mean = round(mean(Post_leader,           na.rm = TRUE), 2),
    leader_sd   = round(sd(Post_leader,             na.rm = TRUE), 2),
    n           = n(),
    .groups     = "drop"
  ) %>%
  print()
```

6.2 Exploratory analysis - linear mixed model for Figure 7
```{r}
mv2_model <- mv2 %>%
  filter(
    Gender_choice %in% c("Man", "Woman"),
    !is.na(Age)
  ) %>%
  mutate(
    site             = interaction(Language, Location, drop = TRUE),
    group            = factor(group, levels = c("C", "S", "R")),
    Rate_familiarity = replace_na(Rate_familiarity, 0)
  )

cat("Rows after filtering：", nrow(mv2_model), "\n")
mv2_model %>% count(group) %>% print()

mv2_model_scaled <- mv2_model %>%
  mutate(
    across(c(pre_bonding_score, post_bonding_score,
             Post_synchronization, Post_enjoyment_task,
             Post_leader, Pre_outgoing, Age,
             Rate_familiarity, Num_of_participants),
           ~ scale(.)[,1])
  )

group_labels <- c("C" = "Conversation", "S" = "Singing", "R" = "Recitation")

var_recode <- c(
  pre_bonding_score     = "Pre-bonding",
  Post_synchronization  = "Synchronisation",
  Post_enjoyment_task   = "Enjoyment",
  Post_leader           = "Leadership",
  Pre_outgoing          = "Extraversion",
  Rate_familiarity      = "Prior familiarity",
  Age                   = "Age",
  Gender_choiceWoman    = "Gender (Female vs. Male)",
  Num_of_participants   = "Group size"
)

plot_list <- list()

for (g in c("S", "C", "R")) {
  sub <- mv2_model_scaled %>% filter(group == g)

  m <- lmer(
    post_bonding_score ~ pre_bonding_score +
      Post_synchronization +
      Post_enjoyment_task +
      Post_leader +
      Pre_outgoing + Age + Gender_choice +
      Rate_familiarity + Num_of_participants +
      (1 | site),
    data = sub,
    na.action = na.exclude,
    REML = TRUE
  )

  print(summary(m))

  cat("\n========================================\n")
  cat("Group:", group_labels[g], "| n =", nrow(sub), "\n")
  cat("========================================\n")

  broom.mixed::tidy(m, effects = "fixed", conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      term_clean = dplyr::recode(term, !!!var_recode),
      across(where(is.numeric), ~round(., 3)),
      sig = case_when(
        p.value < 0.001 ~ "***",
        p.value < 0.01  ~ "**",
        p.value < 0.05  ~ "*",
        TRUE            ~ "ns"
      )
    ) %>%
    dplyr::select(term_clean, estimate, std.error, conf.low, conf.high,
                  statistic, p.value, sig) %>%
    print()

  fixed_order <- c(
    "Extraversion",
    "Prior familiarity",
    "Gender (Female vs. Male)",
    "Age",
    "Group size",
    "Leadership",
    "Enjoyment",
    "Synchronisation",
    "Pre-bonding"
  )

  tidy_g <- broom.mixed::tidy(m, effects = "fixed", conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      term_clean = dplyr::recode(term, !!!var_recode),
      point_color = case_when(
        term == "pre_bonding_score" ~ "baseline",
        term %in% c("Pre_outgoing", "Rate_familiarity",
                    "Age", "Gender_choiceWoman") ~ "control",
        TRUE ~ "task"
      )
    ) %>%
    mutate(term_clean = factor(term_clean, levels = fixed_order))

  label_colors <- tidy_g %>%
    mutate(color = case_when(
      point_color == "baseline" ~ "#2C7BB6",
      point_color == "control"  ~ "#E69F00",
      point_color == "task"     ~ "#C0392B"
    )) %>%
    pull(color)

  annotations <- c("S" = "A", "C" = "B", "R" = "C")

  p_g <- ggplot(tidy_g, aes(x = estimate, y = term_clean)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
    geom_errorbarh(aes(xmin = conf.low, xmax = conf.high,
                       color = point_color),
                   height = 0.2, linewidth = 1.0) +
    geom_point(aes(color = point_color, fill = point_color),
               shape = 23, size = 5, stroke = 0.4) +
    geom_text(aes(label = sprintf("%.2f", estimate)),
              hjust = -0.2, vjust = -0.5, size = 6,
              color = "black", family = "sans", fontface = "bold") +
    scale_color_manual(
      values = c("baseline" = "#2C7BB6",
                 "task"     = "#C0392B",
                 "control"  = "#E69F00"),
      labels = c("baseline" = "Baseline covariate",
                 "task"     = "Explanatory variables",
                 "control"  = "Control variables"),
      breaks = c("baseline", "task", "control"),
      name   = NULL
    ) +
    scale_fill_manual(
      values = c("baseline" = "#2C7BB6",
                 "task"     = "#C0392B",
                 "control"  = "#E69F00"),
      labels = c("baseline" = "Baseline covariate",
                 "task"     = "Explanatory variables",
                 "control"  = "Control variables"),
      breaks = c("baseline", "task", "control"),
      name   = NULL
    ) +
    scale_x_continuous(
      breaks = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7),
      limits = c(-0.3, 0.7),
      labels = c("-0.3", "-0.2", "-0.1", "0", "0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7")
    ) +
    labs(
      title = group_labels[g],
      x     = if (g == "R") "Standardized Estimate (β)" else "",
      y     = NULL
    ) +
    theme_classic() +
    theme(
      plot.title    = element_text(size = 20, face = "bold", hjust = 0.5, family = "sans"),
      axis.text.y   = element_text(size = 18, hjust = 1, family = "sans",
                                    face = "bold", color = "black"),
      axis.ticks.y  = element_line(),
      axis.line.x   = element_line(color = "black"),
      axis.line.y   = element_line(color = "black"),
      axis.text.x   = element_text(size = 18, family = "sans"),
      legend.position = "right",
      legend.text     = element_text(size = 16, family = "sans"),
      legend.key.size = unit(0.8, "cm"),
      axis.title.x  = element_text(size = 20, face = "bold", family = "sans"),
      plot.margin   = margin(10, 20, 10, 10)
    )

  plot_list[[g]] <- p_g
}

plot_list[["S"]] <- plot_list[["S"]] + theme(legend.position = "none")
plot_list[["R"]] <- plot_list[["R"]] + theme(legend.position = "none")

combined <- plot_list[["S"]] / plot_list[["C"]] / plot_list[["R"]]

ggsave(
  filename = "/Users/betty/Desktop/Manyvoices2/Results/Figure/forest_all_groups_withgroupsize.png",
  plot = combined,
  width = 13, height = 17, dpi = 300
)
```



6.3 Correlation among variables for Figure S7
```{r}

corr_list <- list()

for (g in c("S", "C", "R")) {
  sub <- mv2_model_scaled %>% filter(group == g)

  vars <- sub %>%
    dplyr::select(
      pre_bonding_score, Post_synchronization, Post_enjoyment_task,
      Post_leader, Pre_outgoing, Age, Rate_familiarity, Num_of_participants
    ) %>%
    na.omit()

  colnames(vars) <- c(
    "Pre-bonding", "Synchronisation", "Enjoyment",
    "Leadership", "Extraversion", "Age",
    "Prior familiarity", "Group size"
  )

  corr_matrix <- cor(vars)

  corr_list[[g]] <- ggcorrplot(
    corr_matrix,
    method   = "circle",
    type     = "lower",
    lab      = TRUE,
    lab_size = 4,
    colors   = c("#2C7BB6", "white", "#C0392B"),
    title    = group_labels[g],
    ggtheme  = theme_classic()
  ) +
  theme(
    plot.title  = element_text(size = 16, face = "bold", hjust = 0.5),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 12)
  )
}

# 横排拼合
corr_combined <- corr_list[["S"]] / corr_list[["C"]] / corr_list[["R"]]

ggsave(
  "/Users/betty/Desktop/Manyvoices2/Results/Figure/corr_all_groups.png",
  plot = corr_combined,
  width = 7, height = 12, dpi = 300
)

```

6.4 Linear mixed-effects model results in Table S5-S13. 
```{r}

mv2_model_scaled <- mv2_model %>%
  mutate(
    across(c(pre_bonding_score, post_bonding_score,
             Post_synchronization, Post_enjoyment_task, Post_leader,
             Post_difficult_task, Post_embarrassment_task, Post_follow_instruction,
             Pre_outgoing, Age, Rate_familiarity, Num_of_participants),
           ~ scale(.)[,1])
  )

group_labels <- c("C" = "Conversation", "S" = "Singing", "R" = "Recitation")

var_recode_3 <- c(
  pre_bonding_score     = "Pre-bonding",
  Age                   = "Age",
  Gender_choiceWoman    = "Gender (Female vs. Male)",
  Rate_familiarity      = "Prior familiarity",
  Pre_outgoing          = "Extraversion",
  Num_of_participants   = "Group size",
  Post_synchronization  = "Synchronisation",
  Post_enjoyment_task   = "Enjoyment",
  Post_leader           = "Leadership"
)

var_recode_6 <- c(
  var_recode_3,
  Post_difficult_task     = "Difficulty",
  Post_embarrassment_task = "Embarrassment",
  Post_follow_instruction = "Instruction following"
)

get_model_stats <- function(m, model_name, group_name) {
  g   <- broom.mixed::glance(m)
  r2  <- MuMIn::r.squaredGLMM(m)
  vc  <- as.data.frame(VarCorr(m))

  var_site     <- round(vc$vcov[vc$grp == "site"],     3)
  var_residual <- round(vc$vcov[vc$grp == "Residual"], 3)

  data.frame(
    Group        = group_name,
    Model        = model_name,
    R2m          = round(r2[1, "R2m"], 3),
    R2c          = round(r2[1, "R2c"], 3),
    AIC          = round(g$AIC, 1),
    BIC          = round(g$BIC, 1),
    logLik       = round(g$logLik, 1),
    Var_site     = var_site,
    SD_site      = round(sqrt(var_site), 3),
    Var_residual = var_residual,
    SD_residual  = round(sqrt(var_residual), 3),
    df.residual  = g$df.residual
  )
}

extract_beta <- function(m_std) {
  broom.mixed::tidy(m_std, effects = "fixed") %>%
    filter(term != "(Intercept)") %>%
    dplyr::select(term, beta = estimate)
}

table1_list <- list()  # 4 variables: model comparison
table2_list <- list()  # 4 variables: Full model
table3_list <- list()  # 7 variables: model comparison
table4_list <- list()  # 7 variables: Full model


for (g in c("S", "C", "R")) {
  sub_raw <- mv2_model        %>% filter(group == g)
  sub_std <- mv2_model_scaled %>% filter(group == g)

  cat("\n========================================\n")
  cat("Group:", group_labels[g], "| n =", nrow(sub_raw), "\n")
  cat("========================================\n")

  # ---------------- Four explanatory variables ----------------
  m1a <- lmer(post_bonding_score ~ pre_bonding_score + (1 | site),
              data = sub_raw, na.action = na.exclude, REML = TRUE)

  m2a <- lmer(post_bonding_score ~ pre_bonding_score +
                Age + Gender_choice + Rate_familiarity + Pre_outgoing +
                (1 | site),
              data = sub_raw, na.action = na.exclude, REML = TRUE)

  m3a <- lmer(post_bonding_score ~ pre_bonding_score +
                Age + Gender_choice + Rate_familiarity + Pre_outgoing +
                Num_of_participants +
                Post_synchronization + Post_enjoyment_task + Post_leader +
                (1 | site),
              data = sub_raw, na.action = na.exclude, REML = TRUE)

  m3a_std <- lmer(post_bonding_score ~ pre_bonding_score +
                Age + Gender_choice + Rate_familiarity + Pre_outgoing +
                Num_of_participants +
                Post_synchronization + Post_enjoyment_task + Post_leader +
                (1 | site),
              data = sub_std, na.action = na.exclude, REML = TRUE)

  table1_list[[g]] <- bind_rows(
    get_model_stats(m1a, "Model 1: Baseline only",   group_labels[g]),
    get_model_stats(m2a, "Model 2: + Controls",      group_labels[g]),
    get_model_stats(m3a, "Model 3: + Task (3 vars)", group_labels[g])
  )
  cat("\n--- Table 1:", group_labels[g], "---\n"); print(table1_list[[g]])

  beta_3 <- extract_beta(m3a_std)

  table2_list[[g]] <- broom.mixed::tidy(m3a, effects = "fixed", conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    left_join(beta_3, by = "term") %>%
    mutate(
      Group      = group_labels[g],
      term_clean = dplyr::recode(term, !!!var_recode_3),
      across(where(is.numeric), ~round(., 3)),
      sig = case_when(
        p.value < 0.001 ~ "***", p.value < 0.01 ~ "**",
        p.value < 0.05  ~ "*",   TRUE ~ ""
      )
    ) %>%
    dplyr::select(Group, term_clean, B = estimate, SE = std.error, beta,
                  t = statistic, conf.low, conf.high, p.value, sig)
  cat("\n--- Table 2:", group_labels[g], "---\n"); print(table2_list[[g]])

  # ---------------- Seven explanatory variables (baseline/controls are the same as the 3-variable version, reuse directly) ----------------
  m1b <- m1a
  m2b <- m2a

  m3b <- lmer(post_bonding_score ~ pre_bonding_score +
                Age + Gender_choice + Rate_familiarity + Pre_outgoing +
                Num_of_participants +
                Post_synchronization + Post_enjoyment_task + Post_leader +
                Post_difficult_task + Post_embarrassment_task + Post_follow_instruction +
                (1 | site),
              data = sub_raw, na.action = na.exclude, REML = TRUE)

  m3b_std <- lmer(post_bonding_score ~ pre_bonding_score +
                Age + Gender_choice + Rate_familiarity + Pre_outgoing +
                Num_of_participants +
                Post_synchronization + Post_enjoyment_task + Post_leader +
                Post_difficult_task + Post_embarrassment_task + Post_follow_instruction +
                (1 | site),
              data = sub_std, na.action = na.exclude, REML = TRUE)

  table3_list[[g]] <- bind_rows(
    get_model_stats(m1b, "Model 1: Baseline only",   group_labels[g]),
    get_model_stats(m2b, "Model 2: + Controls",      group_labels[g]),
    get_model_stats(m3b, "Model 3: + Task (6 vars)", group_labels[g])
  )
  cat("\n--- Table 3:", group_labels[g], "---\n"); print(table3_list[[g]])

  beta_6 <- extract_beta(m3b_std)

  table4_list[[g]] <- broom.mixed::tidy(m3b, effects = "fixed", conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    left_join(beta_6, by = "term") %>%
    mutate(
      Group      = group_labels[g],
      term_clean = dplyr::recode(term, !!!var_recode_6),
      across(where(is.numeric), ~round(., 3)),
      sig = case_when(
        p.value < 0.001 ~ "***", p.value < 0.01 ~ "**",
        p.value < 0.05  ~ "*",   TRUE ~ ""
      )
    ) %>%
    dplyr::select(Group, term_clean, B = estimate, SE = std.error, beta,
                  t = statistic, conf.low, conf.high, p.value, sig)
  cat("\n--- Table 4:", group_labels[g], "---\n"); print(table4_list[[g]])
}


# 3. Combine outputs

cat("\n\n=== Table 1: Four explanatory variables - Model comparison ===\n"); bind_rows(table1_list) %>% print()
cat("\n=== Table 2: Four explanatory variables - Full Model ===\n");         bind_rows(table2_list) %>% print()
cat("\n=== Table 3: Seven explanatory variables - Model comparison ===\n");     bind_rows(table3_list) %>% print()
cat("\n=== Table 4: Seven explanatory variables - Full Model ===\n");           bind_rows(table4_list) %>% print()
```




7.1 Public goods game - Figure 8 
```{r}
mv2_clean_cor <- mv2 %>%
  filter(!is.na(Public_goods_game), !is.na(post_bonding_score), !is.na(group))

group_labels <- c("C" = "Conversation", "S" = "Singing", "R" = "Recitation")
group_colors <- c("C" = "#D95F02", "S" = "#1B9E77", "R" = "#7570B3")


cat("=== PGG Descriptive Statistics ===\n")
mv2_clean_cor %>%
  group_by(group) %>%
  summarise(
    mean_pgg = round(mean(Public_goods_game, na.rm = TRUE), 2),
    sd_pgg   = round(sd(Public_goods_game,   na.rm = TRUE), 2),
    n        = n(),
    .groups  = "drop"
  ) %>%
  mutate(group = case_when(
    group == "C" ~ "Conversation",
    group == "S" ~ "Singing",
    group == "R" ~ "Recitation"
  )) %>%
  print()

plot_list_nox  <- list()
cor_results_list <- list()  

for (g in c("S", "C", "R")) {
  sub <- mv2_clean_cor %>% filter(group == g)

  cor_test <- cor.test(sub$Public_goods_game, sub$post_bonding_score,
                       method = "spearman")
  p_display <- ifelse(cor_test$p.value < .001, "< .001",
                      sprintf("= %.3f", cor_test$p.value))
  cat("\nGroup:", group_labels[g],
      "| rho =", round(cor_test$estimate, 3),
      "| p", p_display,
      "| n =", nrow(sub), "\n")

  cor_results_list[[g]] <- data.frame(
    Group   = group_labels[g],
    rho     = round(as.numeric(cor_test$estimate),  3),
    S_stat  = round(as.numeric(cor_test$statistic), 1),
    p_value = round(cor_test$p.value, 4),
    n       = nrow(sub)
  )

  cor_label <- sprintf("ρ = %.2f", cor_test$estimate)

  p_main <- ggplot(sub, aes(x = Public_goods_game, y = post_bonding_score)) +
    geom_point(color = group_colors[g], alpha = 0.5, size = 2) +
    geom_smooth(method = "lm", color = "black", se = TRUE, linewidth = 0.8) +
    annotate("text",
             x = min(sub$Public_goods_game, na.rm = TRUE),
             y = max(sub$post_bonding_score, na.rm = TRUE),
             label = cor_label, hjust = 0, vjust = 1,
             size = 7, fontface = "bold") +
    labs(
      title = group_labels[g],
      x = if (g == "C") "Public Goods Game Value" else "",
      y = if (g == "S") "Post Bonding Score" else ""
    ) +
    theme_classic() +
    theme(
      plot.title    = element_text(face = "bold", hjust = 0.5, size = 24, family = "sans"),
      axis.title.x  = element_text(size = 22, face = "bold"),
      axis.title.y  = element_text(size = 22, face = "bold"),
      axis.text     = element_text(size = 22),
      axis.line     = element_blank(),
      panel.border  = element_rect(color = "black", fill = NA, linewidth = 0.8),
      panel.background = element_rect(fill = "white", color = NA),
      plot.background  = element_rect(fill = "white", color = NA)
    )

  p_marginal <- ggMarginal(
    p_main,
    type  = "densigram",
    fill  = group_colors[g],
    alpha = 0.5,
    color = "gray30",
    bins  = 20
  )

  plot_list_nox[[g]] <- p_marginal
}


cor_results <- bind_rows(cor_results_list)
cat("\n=== Spearman Correlation Results (PGG vs Post Bonding Score) ===\n")
print(cor_results)


combined <- gridExtra::grid.arrange(
  plot_list_nox[["S"]],
  plot_list_nox[["C"]],
  plot_list_nox[["R"]],
  ncol = 3
)

ggsave(
  filename = "/Users/betty/Desktop/Manyvoices2/Results/Figure/PGG_bonding_combined.png",
  plot = combined,
  width = 15, height = 5, dpi = 300
)

cat("\nDone. Figures saved.\n")
```


7.2 Public goods game - effects of age and gender on 
```{r}

if (!"site" %in% names(mv2)) {
  mv2 <- mv2 %>% mutate(site = paste(Language, Location, sep = " - "))
}

pgg_data <- mv2 %>%
  filter(Gender_choice %in% c("Man", "Woman")) %>%
  filter(!is.na(Public_goods_game), !is.na(Age), !is.na(group)) %>%
  mutate(
    site          = factor(site),
    group         = factor(group, levels = c("S", "C", "R")),
    Gender_choice = factor(Gender_choice, levels = c("Woman", "Man"))
  )

## 2. Fit one LMM per group, and pull out fixed effects + 95% Wald CIs

run_group_lmm <- function(dat, group_label) {
  cat(sprintf("\n============================================================\n"))
  cat(sprintf("Group: %s  (n = %d, %d sites)\n",
              group_label, nrow(dat), length(unique(dat$site))))
  cat(sprintf("============================================================\n"))

  m <- lmerTest::lmer(
    Public_goods_game ~ Age + Gender_choice + (1 | site),
    data = dat,
    REML = TRUE
  )

  print(summary(m))

  if (isSingular(m)) {
    cat("  [!] Note: this model has a singular fit (random-intercept variance\n",
        "      near zero) -- with few sites per group this is common; the\n",
        "      fixed-effect estimates are still usable but treat the random\n",
        "      effect itself cautiously, and consider whether (1 | site) is\n",
        "      really needed for this subset.\n", sep = "")
  }

  ci <- confint(m, method = "Wald", parm = "beta_")
  cat("\n95% Wald confidence intervals:\n")
  print(ci)

  list(model = m, ci = ci)
}

group_labels <- c(S = "Singing", C = "Conversation", R = "Recitation")

models_by_group <- list()
fixed_tbls       <- list()

for (g in c("S", "C", "R")) {
  dat_g  <- pgg_data %>% filter(group == g)
  fit_g  <- run_group_lmm(dat_g, group_labels[[g]])
  m_g    <- fit_g$model
  ci_g   <- as.data.frame(fit_g$ci)
  models_by_group[[g]] <- m_g

  tbl <- as.data.frame(summary(m_g)$coefficients)
  tbl$term  <- rownames(tbl)
  rownames(tbl) <- NULL

  ci_g$term <- rownames(ci_g)
  names(ci_g)[names(ci_g) == "2.5 %"]  <- "CI_low"
  names(ci_g)[names(ci_g) == "97.5 %"] <- "CI_high"
  rownames(ci_g) <- NULL

  tbl <- tbl %>%
    dplyr::left_join(ci_g, by = "term") %>%
    dplyr::mutate(group = group_labels[[g]]) %>%
    dplyr::select(group, term, Estimate, `Std. Error`, CI_low, CI_high,
                  df, `t value`, `Pr(>|t|)`)

  fixed_tbls[[g]] <- tbl
}

## 3. Combine + save

all_fixed_tbl <- dplyr::bind_rows(fixed_tbls)

all_fixed_tbl <- all_fixed_tbl %>%
  dplyr::group_by(term) %>%
  dplyr::mutate(p_FDR_across_groups = p.adjust(`Pr(>|t|)`, method = "BH")) %>%
  dplyr::ungroup()

cat("\n\n============================================================\n")
cat("FIXED EFFECTS + 95% CI, ALL THREE GROUP-SPECIFIC MODELS\n")
print(all_fixed_tbl)

```



8. Expectancy effect 
```{r}
mv2_cleaned_coding <- read.csv("/Users/betty/Desktop/Manyvoices2/mv2_cleaned_coding_merged.csv")

mv2_cleaned_coding <- mv2_cleaned_coding %>%
  filter(
    pre_bonding_score <= 80,
    Post_attention_check >= 50
  )

coding_data <- mv2_cleaned_coding %>%
  dplyr::select(Jia_coding, Maite_coding, Final_agreed_coding) %>%
  na.omit()

cat("number of rows:", nrow(coding_data), "\n")

group_labels <- c("C" = "Conversation", "S" = "Singing", "R" = "Recitation")

coding_by_group <- mv2_cleaned_coding %>%
  filter(!is.na(Final_agreed_coding), !is.na(group)) %>%
  count(group, Final_agreed_coding, name = "n") %>%
  tidyr::complete(group, Final_agreed_coding, fill = list(n = 0)) %>%  # 
  group_by(group) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  ungroup() %>%
  mutate(group_label = group_labels[group]) %>%
  arrange(group, Final_agreed_coding)

cat("=== Final_agreed_coding distribution by group (long format) ===\n")
print(coding_by_group)

# Table 2
coding_wide <- coding_by_group %>%
  mutate(cell = sprintf("%d (%.1f%%)", n, pct)) %>%
  dplyr::select(group_label, Final_agreed_coding, cell) %>%
  tidyr::pivot_wider(names_from = group_label, values_from = cell)

cat("\n=== Final_agreed_coding distribution by group (wide format) ===\n")
print(coding_wide)

# Results for inter-coder reliability

cat("\n========== Jia vs Maite ==========\n")
kappa_jia_maite <- kappa2(coding_data[, c("Jia_coding", "Maite_coding")], 
                           weight = "unweighted")
print(kappa_jia_maite)

cat("\n========== Jia vs Final ==========\n")
kappa_jia_final <- kappa2(coding_data[, c("Jia_coding", "Final_agreed_coding")], 
                           weight = "unweighted")
print(kappa_jia_final)

cat("\n========== Maite vs Final ==========\n")
kappa_maite_final <- kappa2(coding_data[, c("Maite_coding", "Final_agreed_coding")], 
                             weight = "unweighted")
print(kappa_maite_final)


cat("\n========== Kappa results ==========\n")
kappa_summary <- data.frame(
  Comparison = c("Jia vs Maite", "Jia vs Final", "Maite vs Final"),
  Kappa      = round(c(kappa_jia_maite$value,
                       kappa_jia_final$value,
                       kappa_maite_final$value), 3),
  p_value    = round(c(kappa_jia_maite$p.value,
                       kappa_jia_final$p.value,
                       kappa_maite_final$p.value), 3)
) %>%
  mutate(
    interpretation = case_when(
      Kappa < 0.20 ~ "Slight",
      Kappa < 0.40 ~ "Fair",
      Kappa < 0.60 ~ "Moderate",
      Kappa < 0.80 ~ "Substantial",
      TRUE         ~ "Almost perfect"
    )
  )

print(kappa_summary)

cat("\n========== number of inconsistent cases ==========\n")

cat("\nJia vs Maite:\n")
disagree_jia_maite <- coding_data %>%
  filter(Jia_coding != Maite_coding)
cat("non consistent:", nrow(disagree_jia_maite), "/ total:", nrow(coding_data), 
    "( ", round(nrow(disagree_jia_maite)/nrow(coding_data)*100, 1), "% )\n")

cat("\nJia vs Final:\n")
disagree_jia_final <- coding_data %>%
  filter(Jia_coding != Final_agreed_coding)
cat("not consistent:", nrow(disagree_jia_final), "/ total:", nrow(coding_data),
    "( ", round(nrow(disagree_jia_final)/nrow(coding_data)*100, 1), "% )\n")

cat("\nMaite vs Final:\n")
disagree_maite_final <- coding_data %>%
  filter(Maite_coding != Final_agreed_coding)
cat("not consistent:", nrow(disagree_maite_final), "/ total:", nrow(coding_data),
    "( ", round(nrow(disagree_maite_final)/nrow(coding_data)*100, 1), "% )\n")
```



Below are analysis covered in Supplementary materials
9.1 Demographic information - Age, Gender
```{r}
# Age
# Mean and SD across the mv2 sample
age_summary <- mv2 %>%
  summarise(
    mean_age = mean(Age, na.rm = TRUE),
    sd_age = sd(Age, na.rm = TRUE),
    min_age = min(Age, na.rm = TRUE),
    max_age = max(Age, na.rm = TRUE)
  )
age_summary

age_summary_by_group <- mv2 %>%
  group_by(group) %>%
  summarise(
    n_total = n(),
    n_valid_age = sum(!is.na(Age)),
    mean_age = mean(Age, na.rm = TRUE),
    sd_age = sd(Age, na.rm = TRUE),
    min_age = min(Age, na.rm = TRUE),
    max_age = max(Age, na.rm = TRUE),
    .groups = "drop"
  )
age_summary_by_group
# age group classified as four categories: 18-35, 36-60, >60, NA
mv2 <- mv2 %>%
  mutate(
    age_group2 = case_when(
      is.na(Age) ~ "NA",
      Age >= 18 & Age <= 35 ~ "18–35",
      Age >= 36 & Age <= 60 ~ "36–60",
      Age > 60 ~ ">60"
    )
  )
# Number of participants in different age groups and according proportion
age_dist_all <- mv2 %>%
  group_by(age_group2) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(
    proportion = n / sum(n),
    prop_percent = round(proportion * 100, 1)
  )
age_dist_all
# Number of participants in different age groups and according proportion based on CRS conditions
age_dist <- mv2 %>%
  group_by(group, age_group2) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(group) %>%
  mutate(prop = n / sum(n))
age_dist


#Gender
# Number of participants in different gender groups and according proportion
gender_dist_all <- mv2 %>%
  group_by(Gender_choice) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(
    proportion = n / sum(n),
    prop_percent = round(proportion * 100, 1)
  )
gender_dist_all
# Number of participants in different gender groups and according proportion based on CRS conditions
gender_dist_by_group <- mv2 %>%
  group_by(group, Gender_choice) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(group) %>%
  mutate(
    proportion = n / sum(n),
    prop_percent = round(proportion * 100, 1)
  )
gender_dist_by_group


```


9.2 Religion
```{r}
mv2_cleaned_coding <- read.csv("/Users/betty/Desktop/Manyvoices2/mv2_cleaned_coding_merged.csv")
mv2_cleaned_coding <- mv2_cleaned_coding %>%
  filter(
    pre_bonding_score <= 80,
    Post_attention_check >= 50
  ) 
religion_overall <- mv2_cleaned_coding %>%
  count(recoded_religion) %>%
  mutate(
    proportion = n / sum(n)
  )
religion_overall
religion_by_group <- mv2_cleaned_coding %>%
  group_by(group, recoded_religion) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(group) %>%
  mutate(
    proportion = n / sum(n)
  ) %>%
  ungroup()

religion_by_group

```


9.3. Trained in singing vs. not trained in singing/trained in instrument vs. not trained in instrument
```{r}
singing_years <- mv2_cleaned_coding %>%
  count(coded_singing_years) %>%
  mutate(proportion = n / sum(n))
singing_years

group_singing_years <- mv2_cleaned_coding %>%
  group_by(group, coded_singing_years) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(group) %>%
  mutate(
    proportion = n / sum(n)
  ) %>%
  ungroup()
group_singing_years

instrument_years <- mv2_cleaned_coding %>%
  count(coded_instrument_training_years) %>%
  mutate(proportion = n / sum(n))
instrument_years

group_instrument_years <- mv2_cleaned_coding %>%
  group_by(group, coded_instrument_training_years) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(group) %>%
  mutate(
    proportion = n / sum(n)
  ) %>%
  ungroup()
group_instrument_years
```



10. Internal consistency of bonding scale - reliability and validity testing
```{r}
scale_reliability <- function(data, vars, name) {
  items <- data[, vars, drop = FALSE]
  items <- na.omit(items)         
  n <- nrow(items)
  cat("\n========== ", name, " (n = ", n, ") ==========\n")
  
  # Cronbach's alpha
  alpha_res <- psych::alpha(items, check.keys = TRUE)
  cat("Cronbach's α = ", round(alpha_res$total$raw_alpha, 2), "\n")
  
  # McDonald's omega (total and hierarchical)
  omega_res <- suppressWarnings(psych::omega(items, plot = FALSE))
  cat("McDonald's ω_total = ", round(omega_res$omega.tot, 2), "\n")
  cat("McDonald's ω_hierarchical = ", round(omega_res$omega_h, 2), "\n")
}

pre_vars <- c("Pre_bonding_trust", "Pre_bonding_sameteam", "Pre_bonding_similar",
              "Pre_bonding_ties", "Pre_bonding_common", "Pre_bonding_closeness")
post_vars <- c("Post_bonding_trust", "Post_bonding_sameteam", "Post_bonding_similar",
               "Post_bonding_ties", "Post_bonding_common", "Post_bonding_closeness")
final_vars <- c("Final_bonding_trust", "Final_bonding_sameteam", "Final_bonding_similar",
                "Final_bonding_ties", "Final_bonding_common", "Final_bonding_closeness")

scale_reliability(mv2, pre_vars,   "Pre-bonding")
scale_reliability(mv2, post_vars,  "Post-bonding")
scale_reliability(mv2, final_vars, "Final-bonding")

```


```{r}
group_labels <- c("C" = "Conversation", "S" = "Singing", "R" = "Recitation")
group_colors <- c("C" = "#D95F02", "S" = "#1B9E77", "R" = "#7570B3")
label_levels <- c("Singing", "Conversation", "Recitation")

raw_all  <- list()


for (g in c("S", "R", "C")) {
  sub_df <- mv2 %>% filter(group == g)
  
  
  sub_df$group_label <- factor(group_labels[g], levels = label_levels)
  raw_all[[g]] <- sub_df
}

raw_combined  <- bind_rows(raw_all)

agg_combined <- raw_combined %>%
  group_by(Language, Location, group, group_label) %>%
  summarise(
    post_bonding_score  = mean(post_bonding_score, na.rm = TRUE),
    Num_of_participants = mean(Num_of_participants, na.rm = TRUE),
    .groups = "drop"
  )
lm_labels <- raw_combined %>%
  group_by(group, group_label) %>%
  summarise(
    coef_pre  = round(coef(lm(post_bonding_score ~ pre_bonding_score + Num_of_participants))[2], 2),
    coef_num  = round(coef(lm(post_bonding_score ~ pre_bonding_score + Num_of_participants))[3], 2),
    intercept = round(coef(lm(post_bonding_score ~ pre_bonding_score + Num_of_participants))[1], 2),
    .groups   = "drop"
  ) %>%
  mutate(
  label = sprintf("β = %.2f", coef_num)
)

ggplot() +
  
  geom_point(data = raw_combined,
             aes(x = Num_of_participants, y = post_bonding_score,
                 color = group),
             alpha = 0.15, size = 1.5) +
  
  geom_point(data = agg_combined,
             aes(x = Num_of_participants, y = post_bonding_score,
                 color = group),
             alpha = 0.8, size = 3.5, shape = 18) +
  
  geom_smooth(data = raw_combined,
              aes(x = Num_of_participants, y = post_bonding_score,
                  color = group, fill = group),
              method = "lm", se = TRUE, linewidth = 0.9, alpha = 0.15) +
  
  facet_wrap(~ group_label, ncol = 3) +
  
  scale_color_manual(values = group_colors) +
  scale_fill_manual(values  = group_colors) +
  
  labs(
    x = "Group Size",
    y = "Post Bonding Score"
  ) +
  theme_classic() +
  theme(
    strip.text       = element_text(face = "bold", size = 18),
    strip.background = element_blank(),
    axis.title       = element_text(size = 18, face = "bold"),
    axis.text        = element_text(size = 15),
    axis.line        = element_blank(),
    panel.border     = element_rect(color = "black", fill = NA, linewidth = 0.8),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background  = element_rect(fill = "white", color = NA),
    legend.position  = "none"
  )

ggsave(
  "/Users/betty/Desktop/Manyvoices2/Results/Figure/groupsize_bonding_linear.png",
  width = 12, height = 4.5, dpi = 300
)
```


